The globular cluster system of the Auriga simulations

### 2020-04-10 response_to_referee.tex

\subsection*{Sect. 4 -}
\begin{itemize}
\item We added the mean number of GC candidates compared to the mean number of
star particles in the Auriga L4 galaxies. In addition, Figure 3 now shows the 
number of star particles included in the subset.
\item We clarified at various places whether we mean the mean or median among
the simulations, or if we refer to the absolute value of one of the galaxies.
\item We added the suggestion in the 3rd paragraph of section 4.1.
\item Bimodality in GC systems is now discussed in the introduction.
\item Figure 4 - now has a vertical line to indicate the metallicity cut 
between metal-poor and metal-rich GC subpopulations in the Milky Way.
\item We added a sentence about the cluster formation efficiency model of 
Kruijssen (2012) in the last paragraph of section 4.1.
\item We now show the median instead of the mean for the galactocentric radius in
section 4.2 and Figure 6.
\item Figure 6: no changes were made for rescaling the galaxies (i.e. we still
use the virial radius)
\item Figure 5 and 7: shaded regions now show the 25-75th percentiles.
\item We added a brief discussion of Figure 8.
\item We clarified that we are referring to Figure 5 and Figure 7 for the claims about
the {\it in situ} and accreted component in the third paragraph of section 4.3.
\item Figure 9: The values are removed from the masked upper right corner bins.
\item Figure 2,8,9: The values of the upper and right axes have been removed from
Figure 2 and 9 (observations) for clarity (rather than the suggestion to add 
axis labels and units). However, we did not mask these bins for Figure 8 (Auriga)
because it illustrates our finding that the simulations produce a considerable
amount of mass in GC candidates with low metallicities at large radii.
\end{itemize}

\subsection*{Sect. 5 -}
\begin{itemize}
\item TODO: overall comment
\item We added references to Deason et al. (2015) and Conroy et al. (2019) in
the first paragraph of section 5.1.
\item TODO: bimodality in SLUGGS
\item We still find that the accreted star particles are more metal-poor than 
those that have formed {\textit in situ} if we lower the age cut to 8 or 6 Gyr.
This has been added in section 5.3.
\item We removed the quoted sentence.
\item We clarified that our selection function is inconsistent with the definition
of Kruijssen (2019) for {\textit ex. situ} GC formation.
\end{itemize}

\subsection*{Sect. 6 -}
\begin{itemize}
\item We repeat the goal of the study in section 6.
\item We clarified the 4th point.
\end{itemize}

### 2020-04-10 AurigaGCS.tex
Half-ass the remarks for Section 5 and 6

However, we find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
that the mean metallicity shifts when we split the GC candidates up according 
to birth location (accreted or {\it in~situ}). In particular, the mean values of 
the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
On the other hand, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. The Auriga simulations therefore do not support the view 
that the metal-poor GCs could have only formed in satellites that have later been 
accreted whereas the metal-rich GC subpopulation has only formed {\it in~situ}. 
With this statement, however, we do caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. In fact, our classification might not hold
for Au4-1.

@@

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $r_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower. Our classification as GC candidates could
especially be improved for the accreted subset. For example, we could tag only a
subset of the accreted star particles as GC candidates, where the number
number of GCs is determined by the satellite halo mass, given the 
$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}.

@@

We find that including more recently formed star particles in our subset 
of GC candidates shifts the mean metallicity to higher values. Moreover, the
total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
threshold and moves closer to the dotted line that shows the distribution of
all star particles. However, we notice that the Auriga simulations, on average, 
do not form new stars with a metallicity below [Fe/H] = -1 more recent than 6 Gyr 
ago: the behaviour of Figure~\ref{fig:FeH} does not change for metallicities
below [Fe/H] = -1 when we change the age cut to 8 or 6 Gyr. The qualitative behaviour
of the median distribution of galactocentric radii (Figure~\ref{fig:Rgc}), on 
the other hand, is unaffected by lowering the age cut other than including
more star particles (more mass) which leads to a higher normalisation and
a higher mass ratio with respect to the observed GC systems of the MW and M31.
The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
change when the age cut is lowered to 8 or 6 Gyr.

@@

We investigate statistics of age-selected ($>$~10~Gyr) GC candidates in the 
Auriga simulations and compare the simulations to the MW and M31 GCSs. Based on
our analysis we draw the following conclusions.

>>>>

However, we find that none of the Auriga simulations produces a bimodal 
metallicity distribution for age-selected GC candidates. Interestingly, the 
cross-over point above (below) which the mass-weighted metallicity distribution
of GC candidates is dominated by those that have formed {\it in~situ} (were
accreted) does coincide with the separation between the metal-rich and metal-poor
populations of GCSs at [Fe/H]~=~$-1$, as for the MW. Moreover, we do find 
that the mean metallicity shifts when we split the GC candidates up according 
to birth location (accreted or {\it in~situ}). In particular, the mean values of 
the {\it in~situ} GC candidates are roughly consistent with the metal-rich MW GCs.
On the other hand, we also notice that a substantial number of simulations has similar 
mean values for all GC candidates, and the simulated {\it in~situ} GC candidates 
have larger dispersions than the metal-rich GCs. Moreover, the offset between 
the mean of the metal-rich and metal-poor populations in the MW is $1$ dex, a
factor $2-3$ larger than the offset that we find between the {\it in~situ} and 
accreted populations. However, we caution that \citet{2019MNRAS.486.3134K} suggests 
to reserve the `{\it ex~situ}' classification for accretion after $z=2$, when
the central galaxy has formed and accretion unambigously contributes to the
radially extended halo GC population. Our classification of accreted GC candidates
is thus not consistent with the aforementioned definition because our selection
function mostly includes star particles that have formed before roughly $z=2$.

@@

\subsection{Radial distribution}
\label{sec:discussion_Rgc}
The M31 GCS has a factor 2-3 more GCs at large radii compared to the MW GCS,
which may indicate that M31 has a richer merger history than the MW 
\citep{2016ApJ...824...42C}. In the Auriga simulations we find that the GC 
candidates at radii larger than ${\sim}20$~kpc are indeed dominated by accreted
star particles. However, we select star particles that are bound to the main 
halo and main subhalo, which means that we include particles up to the virial 
radius $r_{200}$. The Auriga simulations have no problem populating the stellar 
halo up to the virial radius, even with our additional age cut. On the other hand, 
the MW and M31 have fewer GCs at large radii. We expect tidal disruption to be
less efficient at larger radii, thus, the formation efficiencies of the accreted 
GC candidates would have to be lower Alternatively, the fraction of old star 
particles in our subset of GC candidates may contain considerably more star 
particles that represent stars in the old stellar halo that have been accreted
during hierarchical buildup of the galaxy. Our classification of GC candidates 
could be improved for the accreted subset in particular. For example, we could 
select only a subset of the accreted star particles as GC candidates where the 
number number of GCs would be determined by the satellite halo mass, given the 
$M_{vir}-N_{\text{gal}}$ correlation found by \citet{2019arXiv190100900B}. However,
we did not include such an analysis in this study.

@@

We find that including more recently formed star particles in our subset 
of GC candidates shifts the mean metallicity to higher values. Moreover, the
total mass in metal-rich ([Fe/H] > -1) GC candidates increases for a lower age 
threshold and moves closer to the dotted line that shows the distribution of
all star particles in Figure~\ref{fig:FeH}. However, 
we notice that the Auriga simulations, on average, do not form new stars with 
a metallicity below [Fe/H]~=~-1 more recent than 6 Gyr ago: the behaviour of 
Figure~\ref{fig:FeH} does not change for metallicities below [Fe/H]~=~-1 when 
we change the age cut to 8 or 6 Gyr, and the slope of the masss ratio for 
metallicities above [Fe/H]~=~-1 is slightly steeper. In addition, we still find
that the accreted GC candidates are more metal-poor than those that have formed 
{\textit in situ}.

The qualitative behaviour of the median distribution of galactocentric radii 
(Figure~\ref{fig:Rgc}) is unaffected by lowering the age cut other than including
more star particles (more mass) which leads to a higher normalisation and
a higher mass ratio with respect to the observed GC systems of the MW and M31.
The qualitative behavour presented in Figure~\ref{fig:Au-FeHRgc-ratio} does not 
change when the age cut is lowered to 8 or 6 Gyr.

@@

We investigate statistics of age-selected ($>$~10~Gyr) GC candidates in the 
Auriga simulations and compare the simulations to the MW and M31 GCSs to test
whether the star formation model implemented for the Auriga simulations can give
rise to metallicity and radial distributions that are consistent with these two
observed GC systems. Based on our analysis we draw the following conclusions.
